\chapter{Conclusion}
\section{Future Work}
This paper leaves many interrogatives open which need to be explored in future works. \\
First of all, in chapter \ref{char_nn}, we only investigated some of the characteristics which neural networks possess and can be correlated with each other. For example, we did not focus on parameters which influence the performances of the networks, like for i.g.learning rate, batch size or throughput. It is left for further studies to identify other characteristics that can be worth studying to find more correlations.\\
In chapter \ref{ana_models}, only techniques related to measuring execution time have been described. However, benchmarks are also used to measure other metrics, such us energy consumption or memory use. It is left for future work to find better techniques to precisely measure and monitor them, as they are also of the highest importance especially for devices with low on-board resources. Furthermore, in this paper we mainly focused on Linux, therefore purposely neglecting other operating systems and micro-controllers and only mentioning some techniques to run benchmarks on mobile devices running Android. 
The study of measurements techniques for other systems is also left for future work. \\
In chapter \ref{ana_char}, we run the benchmarking tool only on two examples. Even though we obtained promising results, we left some interrogatives behind. Firstly, we only run the tool with model from three different CNN architectures. Secondly, we did not investigate how ad-hoc-created models will behave under the conditions we defined. Thirdly, the experiments we made have been run without any augmentation or optimization on both the models and datasets. The models have been trained with the standard batch size, learning rate and were not pre-trained.In addition, they have been trained with full precision. It is left for further investigations to prove if further correlations can be found using different models and different optimizations.\\
Finally, we only investigated if, and which, correlations can be found studying the performance and the behaviour of neural networks. However, this serves only as a starting point for further applications and we did not investigate if these correlations can be used to optimize real world applications. Further research would be needed to prove it. 

\section{Conclusion}